---
title: "Amygdala PPI Plots"
author: "Paul A. Bloom"
date: "March 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(rstanarm)
library(brms)
library(lme4)
source('helper_functions.R')
```

# Pull in and bind together multiverse outputs

Model Coefficients
```{r}
coef_files = paste0('output/ppi/', dir('output/ppi/', pattern = '*coefs*'))


for (ii in 1:length(coef_files)){
  temp_frame = read.csv(coef_files[ii], stringsAsFactors = FALSE)
  if (grepl('robust', coef_files[ii])){
    temp_frame$robust = 'yes'
  }else{
    temp_frame$robust = 'no'
  }
  if (ii == 1){
    ppi_coefs = temp_frame
  }else{
    ppi_coefs = rbind(ppi_coefs, temp_frame)
  }
}



ppi_coefs = ppi_coefs %>%
  mutate(., pipeline = ifelse(startsWith(pipeline, 'deconv'), paste0('fear_', pipeline), pipeline
  ))




# make sure age coefs are named the same thing for quadratic models
ppi_coefs = mutate(ppi_coefs, 
                          term = ifelse(term == 'b_polyageCenter2rawEQTRUE1', 'b_ageCenter', term)) %>%
  dplyr::filter(!grepl('r_', term))
```

Break up by contrast
```{r}
ppi_coefs_neutral = dplyr::filter(ppi_coefs, grepl('neut_deconv', pipeline) |
                                               grepl('neut_no_deconv', pipeline),
                                  !grepl('fear', pipeline))
ppi_coefs_fear_minus_neutral = dplyr::filter(ppi_coefs, grepl('fear_minus_neut_deconv', pipeline) |
                                               grepl('fear_minus_neut_no_deconv', pipeline))

ppi_coefs_fear = dplyr::filter(ppi_coefs, grepl('fear_deconv', pipeline) |
                                 grepl('fear_no_deconv', pipeline))

```

Model Predictions
```{r}
pred_files = paste0('output/ppi/', dir('output/ppi/', pattern = 'pred*'))

for (ii in 1:length(pred_files)){
  temp_frame_pred = read.csv(pred_files[ii], stringsAsFactors = FALSE)
  if (grepl('robust', pred_files[ii])){
    temp_frame_pred$robust = 'yes'
  }else{
    temp_frame_pred$robust = 'no'
  }
  if (ii == 1){
    ppi_preds = temp_frame_pred
  }else{
    ppi_preds = rbind(ppi_preds, temp_frame_pred)
  }
}


ppi_preds = ppi_preds %>%
  mutate(., pipeline = ifelse(startsWith(pipeline, 'deconv'), paste0('fear_', pipeline), pipeline
  ))


ppi_preds_neutral = dplyr::filter(ppi_preds, grepl('neut_deconv', pipeline) |
                                               grepl('neut_no_deconv', pipeline),
                                  !grepl('fear', pipeline))
ppi_preds_fear_minus_neutral = dplyr::filter(ppi_preds, grepl('fear_minus_neut_deconv', pipeline) |
                                               grepl('fear_minus_neut_no_deconv', pipeline))
ppi_preds_fear = dplyr::filter(ppi_preds,grepl('fear_deconv', pipeline) |
                                               grepl('fear_no_deconv', pipeline))
```


```{r}
# Load in raw data
ppi = read.csv('compiled_data/comps_amyg_fear_ppi_master.csv', stringsAsFactors = FALSE)
ppi_all_contrasts = read.csv('compiled_data/comps_amyg_all_contrasts_ppi_master.csv', stringsAsFactors = FALSE)

# Tidy it
ppi_long_fear = ppi %>%
  tidyr::gather(., key = 'pipeline', value = 'ppi', contains('conv'))

ppi_long_neut = ppi_all_contrasts %>%
  dplyr::select(., -contains('fear')) %>%
  tidyr::gather(., key = 'pipeline', value = 'ppi', contains('conv'))
  
ppi_long_fear_minus_neut = ppi_all_contrasts %>%
  dplyr::select(., contains('fear_minus_neut'), name, Subject, 
                wave, Age, Block, group, gender, meanFdIncluded, censoredTR, meanAge,
                motion, ageCenter,prev_studied, scanner, blockBin) %>%
  tidyr::gather(., key = 'pipeline', value = 'ppi', contains('conv'))

# Nest and set indices
ppi_raw_data_fear = ppi_long_fear %>%
  group_by(pipeline) %>%
  nest() %>%
  ungroup() %>%
  mutate(., index = 1:nrow(.)) %>%
  unnest(data)

ppi_raw_data_neut = ppi_long_neut %>%
  group_by(pipeline) %>%
  nest() %>%
  ungroup() %>%
  mutate(., index = 1:nrow(.)) %>%
  unnest(data)

ppi_raw_data_fear_minus_neut = ppi_long_fear_minus_neut %>%
  group_by(pipeline) %>%
  nest() %>%
  ungroup() %>%
  mutate(., index = 1:nrow(.)) %>%
  unnest(data)

```

# SCA Plots

```{r}
# set up fork list
fork_list = c('tstat', 'quadratic', 'random_slopes', 	
              'ctrl_scanner', 'ctrl_block', 'exclude_prev',	'robust',
              'deconvolution', 'mpfc1', 'mpfc2', 'mpfc3', 'mpfc_big')

# age-related change SCA plots
ppi_sca_fear = make_ppi_sca_plot(coefs = ppi_coefs_fear, fork_list = fork_list, contrast_type = 'fear', 
                  plot_title = 'Estimated Age-Related Change\nFear > Baseline Contrast',
                  y_label = 'Estimated Age-Related Change\nFear > Baseline Contrast',term_choice = 'b_ageCenter')

ppi_sca_neut = make_ppi_sca_plot(coefs = ppi_coefs_neutral, fork_list = fork_list, contrast_type = 'neut', 
                  plot_title = 'Estimated Age-Related Change\nNeutral > Baseline Contrast',
                  y_label = 'Estimated Age-Related Change\nNeutral > Baseline Contrast',term_choice = 'b_ageCenter')


ppi_sca_fear_minus_neut = make_ppi_sca_plot(coefs = ppi_coefs_fear_minus_neutral, fork_list = fork_list, contrast_type = 'fear_minus_neut', 
                  plot_title = 'Estimated Age-Related Change\nFear > Neutral Contrast',
                  y_label = 'Estimated Age-Related Change\nFear > Neutral Contrast',term_choice = 'b_ageCenter')


ppi_panel_neut = cowplot::plot_grid(ppi_sca_neut$sca_top, ppi_sca_neut$sca_bottom, ncol = 1, align = "v", axis = 'lr', labels = c('A', 'B'))
ppi_panel_fear_minus_neut = cowplot::plot_grid(ppi_sca_fear_minus_neut$sca_top, ppi_sca_fear_minus_neut$sca_bottom, ncol = 1, align = "v", axis = 'lr', labels = c('A', 'B'))

cowplot::save_plot(ppi_panel_neut, file = 'plots/supplement/gppi_amyg_pfc_linear_neut.png', base_height = 6, base_width = 10)
cowplot::save_plot(ppi_panel_fear_minus_neut, file = 'plots/supplement/gppi_amyg_pfc_linear_fear_minus_neut.png', base_height = 6, base_width = 10)

```
# Fear PPI sca info

```{r}
table(ppi_sca_fear$sca_decision_frame$overlap_0)/nrow(ppi_sca_fear$sca_decision_frame)
1-table(ppi_sca_fear$sca_decision_frame$overlap_0)/nrow(ppi_sca_fear$sca_decision_frame)

ppi_sca_fear$sca_decision_frame %>%
  dplyr::filter(deconvolution == '|') %>%
  group_by(overlap_0) %>%
  summarise(n = n(), freq = n /nrow(.))

ppi_sca_fear$sca_decision_frame %>%
  dplyr::filter(is.na(deconvolution)) %>%
  group_by(overlap_0) %>%
  summarise(n = n(), freq = n /nrow(.), freq_n = 1- freq)


table(ppi_sca_neut$sca_decision_frame$overlap_0) / nrow(ppi_sca_neut$sca_decision_frame)

table(ppi_sca_fear_minus_neut$sca_decision_frame$overlap_0) / nrow(ppi_sca_fear_minus_neut$sca_decision_frame)



```
# Main manuscript PPI figure
```{r}
# ppi preds plot
ppi_raw_data_fear_select = ppi_raw_data_fear %>%
  dplyr::filter(grepl('tstat', pipeline)) %>%
  dplyr::mutate(Deconvolution = ifelse(grepl('no_deconv', pipeline), 'No Deconvolution Step', 'Deconvolution Step'),
                `mPFC ROI` = case_when(
                  grepl('mpfc1', pipeline) ~ 'mPFC 1',
                  grepl('mpfc2', pipeline) ~ 'mPFC 2',
                  grepl('mpfc3', pipeline) ~ 'mPFC 3',
                  grepl('vmpfc', pipeline) ~ 'large vmPFC',
  ))

ppi_preds_fear$age = ppi_preds_fear$ageCenter + ppi_raw_data_fear$meanAge[1]

pred_plot = ppi_preds_fear %>%
  dplyr::filter(model_type == 'modLinear', blockBin == 'first', scanner == '1', robust == 'yes', grepl('tstat', pipeline))  %>%
  dplyr::mutate(Deconvolution = ifelse(grepl('no_deconv', pipeline), 'No Deconvolution Step', 'Deconvolution Step'),
                `mPFC ROI` = case_when(
                  grepl('mpfc1', pipeline) ~ 'mPFC 1',
                  grepl('mpfc2', pipeline) ~ 'mPFC 2',
                  grepl('mpfc3', pipeline) ~ 'mPFC 3',
                  grepl('vmpfc', pipeline) ~ 'large vmPFC',
  )) %>%
  ggplot(data = ., aes(x = age, y = Estimate, color = Deconvolution, fill = Deconvolution)) +
    geom_hline(yintercept = 0, lty = 2) +
    geom_point(data = ppi_raw_data_fear_select, aes(x = Age, y= ppi), alpha = .2) +
    geom_line(data = ppi_raw_data_fear_select, aes(x = Age, y= ppi, group = interaction(Subject, Deconvolution)), alpha = .2) +
    geom_ribbon(aes(ymin = Q2.5, ymax = Q97.5), color = NA, alpha = .4) +
    geom_line(lwd = 1) +
    facet_grid(~`mPFC ROI`) +
    theme_bw() +
    theme(panel.grid.minor = element_blank(), legend.position = 'bottom',
          legend.title = element_blank()) +
    labs(x = 'Age (in years)', y = 'Estimated Amyg-mPFC PPI') 

pfc_roi = ggdraw() + draw_image("plots/roi/pfc_crop_2.png")

left_panel = cowplot::plot_grid(pfc_roi, pred_plot, cols = 1, labels = c('A', 'B'), rel_heights = c(1,2))

ppi_figure1 = cowplot::plot_grid(left_panel, ppi_sca_fear$sca_panel)
cowplot::save_plot(ppi_figure1, file = 'plots/ppi/ppi_fig3.pdf', base_height = 6, base_width = 14)
```


```{r}
save(ppi_preds_fear, ppi_preds_neutral, ppi_preds_fear_minus_neutral,
     ppi_sca_fear, ppi_sca_neut, ppi_sca_fear_minus_neut,
     ppi_raw_data_fear, ppi_raw_data_neut, ppi_raw_data_fear_minus_neut, file = 'output/ppi/ppi_summary_outputs.rda')
```




# ppi quadratic age effects

```{r}
ppi_sca_fear_quadratic= make_ppi_sca_plot(coefs = ppi_coefs_fear, fork_list = fork_list, contrast_type = 'fear_quadratic', 
                  plot_title = 'Quadratic Age-Related Change\nFear > Baseline Contrast',
                  y_label = 'Quadratic Age-Related Change\nFear > Baselinel Contrast',term_choice = 'b_polyageCenter2rawEQTRUE2')


cowplot::plot_grid(ppi_sca_fear_quadratic$sca_top, 
                   ppi_sca_fear_quadratic$sca_bottom, nrow = 2, align = 'v', axis = 'lr', labels = c('A', 'B'))

ppi_sca_neut_quadratic= make_ppi_sca_plot(coefs = ppi_coefs_neutral, fork_list = fork_list, contrast_type = 'neut_quadratic', 
                  plot_title = 'Quadratic Age-Related Change\nNeutral > Baseline Contrast',
                  y_label = 'Quadratic Age-Related Change\nNeutral > Baselinel Contrast',term_choice = 'b_polyageCenter2rawEQTRUE2')

ppi_sca_fear_minus_neut_quadratic= make_ppi_sca_plot(coefs = ppi_coefs_fear_minus_neutral, fork_list = fork_list, contrast_type = 'fear_minus_neutquadratic', 
                  plot_title = 'Quadratic Age-Related Change\nFear > Neutral Contrast',
                  y_label = 'Quadratic Age-Related Change\nFear > Neutral Contrast',term_choice = 'b_polyageCenter2rawEQTRUE2')


save_plot(cowplot::plot_grid(ppi_sca_fear_quadratic$sca_top, 
                   ppi_sca_fear_quadratic$sca_bottom, nrow = 2, align = 'v', axis = 'lr', labels = c('A', 'B')),
          filename = 'plots/supplement/gppi_amyg_pfc_quadratic_fear.png', base_height = 6, base_width = 9)

save_plot(cowplot::plot_grid(ppi_sca_neut_quadratic$sca_top, 
                   ppi_sca_neut_quadratic$sca_bottom, nrow = 2, align = 'v', axis = 'lr', labels = c('A', 'B')),
          filename = 'plots/supplement/gppi_amyg_pfc_quadratic_neut.png', base_height = 6, base_width = 9)

save_plot(cowplot::plot_grid(ppi_sca_fear_minus_neut_quadratic$sca_top, 
                   ppi_sca_fear_minus_neut_quadratic$sca_bottom, nrow = 2, align = 'v', axis = 'lr', labels = c('A', 'B')),
          filename = 'plots/supplement/gppi_amyg_pfc_quadratic_fear_minus_neut.png', base_height = 6, base_width = 9)


table(ppi_sca_fear_quadratic$sca_decision_frame$overlap_0) / nrow(ppi_sca_fear_quadratic$sca_decision_frame)
table(ppi_sca_neut_quadratic$sca_decision_frame$overlap_0) / nrow(ppi_sca_neut_quadratic$sca_decision_frame)
table(ppi_sca_fear_minus_neut_quadratic$sca_decision_frame$overlap_0) / nrow(ppi_sca_fear_minus_neut_quadratic$sca_decision_frame)

```


# gPPI group averaage SCA
```{r}
ppi_mean_models = ppi_all_contrasts %>%
  dplyr::filter(censoredTR <=40) %>%
  pivot_longer(contains('pfc'), names_to = 'pipeline', values_to = 'ppi') %>%
  group_by(pipeline) %>%
  nest() %>%
  mutate(., model = map(data, 
            ~lmer(ppi ~ 1  + (1|Subject), data = .))) %>%
  mutate(., coefs = map(model, ~broom.mixed::tidy(.))) %>%
  dplyr::select(., -data, -model) %>%
  unnest(coefs) %>%
  dplyr::filter(term == '(Intercept)') %>%
  dplyr::mutate(lwr = estimate - 2*std.error,
                upr = estimate + 2*std.error) 


ppi_mean_models = mutate(ppi_mean_models, contrast = case_when(
  grepl('fear', pipeline) & !grepl('neut', pipeline) ~ 'Fear > Baseline',
  grepl('neut', pipeline) & !grepl('fear', pipeline) ~ 'Neutral > Baseline',
  grepl('fear', pipeline) & grepl('neut', pipeline) ~ 'Fear > Neutral'),
  `Deconvolution Step` = ifelse(grepl('no_deconv', pipeline), '-deconv.', '+deconv.'),
  roi = parse_number(pipeline),
  roi = case_when(is.na(roi) ~ 'large vmPFC',
                  roi == 1 ~ 'mPFC 1',
                  roi == 2 ~ 'mPFC 2',
                  roi == 3 ~ 'mPFC 3'
                  ),
  `Scan-level estimate type` = ifelse(grepl('tstat', pipeline), 'T-stat', 'Beta')) %>%
  ungroup() %>%
  group_by(contrast) %>%
  mutate(rank = rank(estimate))

ppi_mean_group_plt = ggplot(ppi_mean_models, aes(x = roi, y = estimate, 
                                                 color = `Deconvolution Step` , shape = `Scan-level estimate type` )) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(position = position_dodge(0.4)) +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0, position = position_dodge(0.4)) +
  facet_grid(~contrast) +
  labs(y = 'Estimated Group Average gPPI with bilateral amygdala', x = 'mPFC ROI') +
  theme_bw() +
  coord_flip() 


  
ggsave(ppi_mean_group_plt, filename = 'plots/supplement/gppi_mean_group_plot.png', height = 4, width = 7)
```

# Analysis of 'physio terms' for task-independent connectivity



Mean physio terms
```{r}
phys = read_csv('compiled_data/comps_amyg_pfc_gppi_phys_terms.csv') %>%
  dplyr::filter(censoredTR <=40)



phys_long = phys %>%
  pivot_longer(contains('pfc'), names_to = 'pipeline', values_to = 'physio') %>%
  group_by(pipeline)

phys_group_means = phys %>%
  pivot_longer(contains('pfc'), names_to = 'pipeline', values_to = 'physio') %>%
  group_by(pipeline) %>%
  nest() %>%
  mutate(., model = map(data, 
            ~lmer(physio ~ 1  + (1|Subject), data = .))) %>%
  mutate(., coefs = map(model, ~broom.mixed::tidy(.))) %>%
  dplyr::select(., -data, -model) %>%
  unnest(coefs) %>%
  dplyr::filter(term == '(Intercept)') %>%
  dplyr::mutate(lwr = estimate - 2*std.error,
                upr = estimate + 2*std.error,
                `Deconvolution Step` = ifelse(grepl('no_deconv', pipeline), '-deconv.', '+deconv.'),
  roi = case_when(
    grepl('mpfc1', pipeline) ~ 'mPFC #1',
    grepl('mpfc2', pipeline) ~ 'mPFC #2',
    grepl('mpfc3', pipeline) ~ 'mPFC #3',
    grepl('vmpfc', pipeline) ~ 'large vmPFC'),
  `Scan-level estimate type` = ifelse(grepl('tstat', pipeline), 'T-stat', 'Beta')) 



gppi_physio_mean = ggplot(phys_group_means, aes(x = `Deconvolution Step`, y = estimate, color = `Scan-level estimate type`)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(position = position_dodge(0.4)) +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0, position = position_dodge(0.4)) +
  theme_bw() +
  facet_grid(cols = vars(roi)) +
  labs(x = '', y = 'Task-independent amygdala-mPFC connectivity\nestimated group averaage')
    
ggsave(gppi_physio_mean, filename = 'plots/supplement/gppi_amyg_pfc_physio_mean.png', height=4, width = 8)


```
Age-related change in physio terms

```{r}
pred_frame = expand.grid(motion = 0, ageCenter = -5:10)

phys_age_coefs = phys %>%
  pivot_longer(contains('pfc'), names_to = 'pipeline', values_to = 'physio') %>%
  group_by(pipeline) %>%
  nest() %>%
  mutate(., model = map(data, 
            ~lmer(physio ~ ageCenter + motion + (1|Subject), data = .))) %>%
  mutate(., coefs = map(model, ~broom.mixed::tidy(.))) %>%
  dplyr::select(., -data, -model) %>%
  unnest(coefs) %>%
  dplyr::filter(term == 'ageCenter') %>%
  dplyr::mutate(lwr = estimate - 2*std.error,
                upr = estimate + 2*std.error,
                `Deconvolution Step` = ifelse(grepl('no_deconv', pipeline), '-deconv.', '+deconv.'),
  roi = case_when(
    grepl('mpfc1', pipeline) ~ 'mPFC #1',
    grepl('mpfc2', pipeline) ~ 'mPFC #2',
    grepl('mpfc3', pipeline) ~ 'mPFC #3',
    grepl('vmpfc', pipeline) ~ 'large vmPFC'),
  `Scan-level estimate type` = ifelse(grepl('tstat', pipeline), 'T-stat', 'Beta')) 


phys_age_pred = phys %>%
  pivot_longer(contains('pfc'), names_to = 'pipeline', values_to = 'physio') %>%
  group_by(pipeline) %>%
  nest() %>%
  mutate(., model = map(data, 
            ~lmer(physio ~ ageCenter + motion + (1|Subject), data = .))) %>%
  mutate(preds = map(model, ~predict(., newdata = pred_frame, re.form = ~0))) 


for (i in 1:nrow(phys_age_pred)){
  pred_grid = phys_age_pred$preds[[i]] %>%
    cbind(pred_frame, .)
  pred_grid$pipeline = phys_age_pred$pipeline[[i]] 
  print(pred_grid)
  
  if (i == 1){
    combined_preds = pred_grid
  }else{
    combined_preds = rbind(combined_preds, pred_grid)
  }
}

combined_preds = mutate(combined_preds, deconv = ifelse(grepl('no_deconv', pipeline), '-deconv', '+deconv'))

phys_age_left =  ggplot(phys_age_coefs, aes(color = `Deconvolution Step`, y = estimate, x = `Scan-level estimate type`)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(position = position_dodge(0.4)) +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0, position = position_dodge(0.4)) +
  theme_bw() +
  facet_grid(cols = vars(roi)) +
  labs(x = '', y = 'Task-independent amygdala-mPFC connectivity\nestimated age-related change')

phys_age_right = ggplot(combined_preds, aes(x = ageCenter + phys$meanAge[1], y = `.`, group = pipeline, color = deconv)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_line() +
  theme_bw() +
  labs(x = 'Age (in years)', y = "Model-estimated task-independent amygdala-mPFC connectivity") +
  theme(legend.position = 'none')



physio_age_plt = cowplot::plot_grid(phys_age_left, phys_age_right, labels = c('A', 'B'))
cowplot::save_plot(physio_age_plt, filename = 'plots/supplement/gppi_physio_age_plt.png', base_height = 6, base_width = 12)
```

# Model the estimates by decision point
```{r}
ppi_sca_fear_frame = ppi_sca_fear$sca_decision_frame
ppi_sca_fear_frame[is.na(ppi_sca_fear_frame)] <- 0
ppi_sca_fear_frame[ppi_sca_fear_frame == '|'] <- 1

ppi_sca_neut_frame = ppi_sca_neut$sca_decision_frame
ppi_sca_neut_frame[is.na(ppi_sca_neut_frame)] <- 0
ppi_sca_neut_frame[ppi_sca_neut_frame == '|'] <- 1

ppi_sca_fear_minus_neut_frame = ppi_sca_fear_minus_neut$sca_decision_frame
ppi_sca_fear_minus_neut_frame[is.na(ppi_sca_fear_minus_neut_frame)] <- 0
ppi_sca_fear_minus_neut_frame[ppi_sca_fear_minus_neut_frame == '|'] <- 1


make_decision_plot_ppi = function(df, contrast){

  meta_model = stan_glm(data = df, estimate ~ tstat + quadratic +
                          random_slopes + ctrl_scanner + ctrl_block +
                          exclude_prev + deconvolution + robust + 
                          mpfc_big + mpfc2 + mpfc3, cores = 4, chains = 4)
  
  summary(meta_model)
  
  fork_fx = brms::posterior_samples(meta_model, pars = fork_list) %>%
    mutate(., index = 1:nrow(.)) %>%
    tidyr::gather(., key = 'fork', value = 'effect', -index) %>%
    mutate(., fork = gsub('1', '', fork)) %>%
    group_by(fork) %>%
    mutate(mean_effect = -1*mean(effect)) %>%
    ungroup() %>%
     mutate(decisiontype = case_when(
        fork %in% c('quadratic', 'random_slopes', 'ctrl_scanner','ctrl_block', 'exclude_prev', 'robust') ~ 'Group-Level\nModel',
        fork %in% c('deconvolution', 'tstat') ~ 'Subject-Level\nModel',
        grepl('pfc', fork) ~ 'mPFC ROI'
      ))
    
  fork_fx$fork  = dplyr::recode(fork_fx$fork, 'tstat' = 'use tstats (vs. beta estimates)',
                                  'exclude_prev' = 'exclude previously analyzed participants (vs. include)',
                                  'quadratic' = 'quadratic age term (vs. none)',
                                  'random_slopes' = 'random intercepts only (vs. random slopes)',
                                  'ctrl_block' = 'covariate for task block (vs. none)',
                                  'ctrl_scanner' = 'covariate for scanner used (vs. none)',
                                  'robust' = 'robust regression (vs. gaussian likelihood)',
                                  'deconvolution' = 'include deconvolution step (vs. none)',
                                  'mpfc3' = 'mPFC #3 (vs. mPFC #1)',
                                  'mpfc_big' = 'large vmPFC (vs. mPFC #1)',
                                  'mpfc2' = 'mPFC #2 (vs. mPFC #1)',
                                )
  
  fork_fx$fork_ordered = reorder(fork_fx$fork,  fork_fx$mean_effect)
    
  fork_fx_summary = fork_fx %>%
      group_by(fork_ordered, decisiontype) %>%
      summarise(median = median(effect),
                lwr_95 = quantile(effect, probs = .025),
                upr_95 = quantile(effect, probs = .975))
  
  decision_plot = ggplot(data = fork_fx, aes(x = fork_ordered, y = effect, fill = decisiontype)) +
      geom_hline(yintercept = 0, lty = 2) +
      geom_flat_violin(color = NA) +
      geom_point(data = fork_fx_summary, aes(x = fork_ordered, y = median)) +
      geom_errorbar(data = fork_fx_summary, aes(x = fork_ordered, y = median, ymin = lwr_95, ymax = upr_95), width = 0) +
      theme_bw() +
      coord_flip() +
      theme(legend.position = 'none') +
      labs(y = 'Difference in age-related change estimate relative to alternative choice\nConditional on all other decision points', 
           x = 'Analysis Choice',
           title = contrast) +
      facet_grid(rows = vars(decisiontype), drop = TRUE, scales = 'free_y', space = 'free_y')
  
  return(decision_plot)
}

fear_decision_plot = make_decision_plot_ppi(df = ppi_sca_fear_frame, contrast = 'Fear > Baseline gPPI')
neut_decision_plot = make_decision_plot_ppi(df = ppi_sca_neut_frame, contrast = 'Neutral > Baseline gPPI')
fear_minus_neut_decision_plot = make_decision_plot_ppi(df = ppi_sca_fear_minus_neut_frame, contrast = 'Fear > Neutral gPPI')


cowplot::save_plot(fear_decision_plot, filename = 'plots/supplement/gppi_fear_age_decision_plot.png', base_height = 5, base_width = 8)
cowplot::save_plot(neut_decision_plot, filename = 'plots/supplement/gppi_neutral_age_decision_plot.png', base_height = 5, base_width = 8)
cowplot::save_plot(fear_minus_neut_decision_plot, filename = 'plots/supplement/gppi_fear_minus_neut_age_decision_plot.png', base_height = 5, base_width = 8)

```
