---
title: "Compile habit"
author: "Paul A. Bloom"
date: "March 2020"
output: html_document
---

# Data setup/cleaning for habituation multiverse

3 types of ways to look at habituation

  * Slopes across trials
  * Halves of trials (first 12, last 12)
  * Single-trial models (i.e. modeling effect of trial #)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(lme4)
library(corrplot)
library(psych)
source('helper_functions.R')
```

# Read in the data and pull together

Get demographic info in
```{r}
demog = read.csv('../2_motion/motionInfoAllEmotions.csv', stringsAsFactors = FALSE) %>%
  dplyr::filter(., runType == 'fear') %>%
  dplyr::select(., name, Subject, wave, Block, Age, group, gender, meanFdIncluded, censoredTR) %>%
  dplyr::mutate(., meanAge = mean(Age), motion = scale(meanFdIncluded), ageCenter = Age - meanAge) # mean-centered age and scaled motion
```

# habit with/without global signal
```{r}
habit_global_signal = read.csv('../8_betaSeries/habituation/allAmygBetas_global_signal.csv', stringsAsFactors = FALSE) %>%
  dplyr::select(., name, trial, 
                bilateral_gsr_fear = fear_betas_bilateral,
                right_gsr_fear = fear_betas_right,
                left_gsr_fear = fear_betas_left,
                bilateral_gsr_neut = neut_betas_bilateral,
                right_gsr_neut = neut_betas_right,
                left_gsr_neut = neut_betas_left) 


habit_no_global_signal = read.csv('../8_betaSeries/habituation/allAmygBetas.csv', stringsAsFactors = FALSE) %>%
  dplyr::select(., name, trial, 
                bilateral_no_gsr_fear = fear_betas_bilateral,
                right_no_gsr_fear = fear_betas_right,
                left_no_gsr_fear = fear_betas_left,
                bilateral_no_gsr_neut = neut_betas_bilateral,
                right_no_gsr_neut = neut_betas_right,
                left_no_gsr_neut = neut_betas_left) 


all_habit = left_join(habit_global_signal, habit_no_global_signal, by = c('name', 'trial')) 

```

# Get slopes across betas and medians for each half of the trials
```{r}
habit_slopes = all_habit %>%
  group_by(name) %>%
  summarise(
            # slopes across trials
            bilateral_gsr_fear_slope = fisherz(cor(bilateral_gsr_fear, trial, method = 'spearman')),
            right_gsr_fear_slope = fisherz(cor(right_gsr_fear, trial, method = 'spearman')),
            left_gsr_fear_slope = fisherz(cor(left_gsr_fear, trial, method = 'spearman')),
            bilateral_no_gsr_fear_slope = fisherz(cor(bilateral_no_gsr_fear, trial, method = 'spearman')),
            right_no_gsr_fear_slope = fisherz(cor(right_no_gsr_fear, trial, method = 'spearman')),
            left_no_gsr_fear_slope = fisherz(cor(left_no_gsr_fear, trial, method = 'spearman')),
            bilateral_gsr_neut_slope = fisherz(cor(bilateral_gsr_neut, trial, method = 'spearman')),
            right_gsr_neut_slope = fisherz(cor(right_gsr_neut, trial, method = 'spearman')),
            left_gsr_neut_slope = fisherz(cor(left_gsr_neut, trial, method = 'spearman')),
            bilateral_no_gsr_neut_slope = fisherz(cor(bilateral_no_gsr_neut, trial, method = 'spearman')),
            right_no_gsr_neut_slope = fisherz(cor(right_no_gsr_neut, trial, method = 'spearman')),
            left_no_gsr_neut_slope = fisherz(cor(left_no_gsr_neut, trial, method = 'spearman')),
            # Half medians
            bilateral_gsr_fear_half1 = median(bilateral_gsr_fear[1:12]),
            bilateral_gsr_fear_half2 = median(bilateral_gsr_fear[13:24]),
            right_gsr_fear_half1 = median(right_gsr_fear[1:12]),
            right_gsr_fear_half2 = median(right_gsr_fear[13:24]),
            left_gsr_fear_half1 = median(left_gsr_fear[1:12]),
            left_gsr_fear_half2 = median(left_gsr_fear[13:24]),
            bilateral_no_gsr_fear_half1 = median(bilateral_no_gsr_fear[1:12]),
            bilateral_no_gsr_fear_half2 = median(bilateral_no_gsr_fear[13:24]),
            right_no_gsr_fear_half1 = median(right_no_gsr_fear[1:12]),
            right_no_gsr_fear_half2 = median(right_no_gsr_fear[13:24]),
            left_no_gsr_fear_half1 = median(left_no_gsr_fear[1:12]),
            left_no_gsr_fear_half2 = median(left_no_gsr_fear[13:24]),
            bilateral_gsr_neut_half1 = median(bilateral_gsr_neut[1:12]),
            bilateral_gsr_neut_half2 = median(bilateral_gsr_neut[13:24]),
            right_gsr_neut_half1 = median(right_gsr_neut[1:12]),
            right_gsr_neut_half2 = median(right_gsr_neut[13:24]),
            left_gsr_neut_half1 = median(left_gsr_neut[1:12]),
            left_gsr_neut_half2 = median(left_gsr_neut[13:24]),
            bilateral_no_gsr_neut_half1 = median(bilateral_no_gsr_neut[1:12]),
            bilateral_no_gsr_neut_half2 = median(bilateral_no_gsr_neut[13:24]),
            right_no_gsr_neut_half1 = median(right_no_gsr_neut[1:12]),
            right_no_gsr_neut_half2 = median(right_no_gsr_neut[13:24]),
            left_no_gsr_neut_half1 = median(left_no_gsr_neut[1:12]),
            left_no_gsr_neut_half2 = median(left_no_gsr_neut[13:24])) %>%
  mutate_if(is.numeric, na_outliers, num_sds = 3) %>%
  mutate_at(vars(matches("half")), scale, center = FALSE)

# reformat halves
habit_halves = habit_slopes %>%
  pivot_longer(contains('half'),
  names_to = c("set", ".value"),
  names_pattern = "(.+)_(.+)") %>%
  dplyr::select(name, set, half1, half2) %>%
  pivot_longer(contains('half'), names_to ='half')

# take out halves from slopes frame
habit_slopes = dplyr::select(habit_slopes, name, contains('slope'))
```

# Single-trial prep
```{r, results='hide', echo=FALSE}
# Remove outliers and scale
all_habit = all_habit %>%
  group_by(name) %>%
  mutate_if(is.numeric, na_outliers, num_sds = 3) %>%
  ungroup() %>%
  mutate_at(vars(matches("gsr")), scale, center = FALSE)

# within-subject mean-centering for single trials
all_habit_within_mean_center = all_habit %>%
  group_by(name) %>%
  mutate_at(vars(matches("gsr")), scale, center = TRUE)

# rename within-subject mean-centered habituation columnds
names(all_habit_within_mean_center)[grepl('gsr', names(all_habit_within_mean_center))] = paste0(names(all_habit_within_mean_center)[grepl('gsr', names(all_habit_within_mean_center))], '_w')


all_habit_trials = left_join(all_habit, all_habit_within_mean_center, by = c('name', 'trial'))
```

# Check correlations in habit metrics
```{r}
habit_cors = cor(dplyr::select(habit_slopes, -name), use = 'complete.obs')
pdf('plots/habit/habit_slope_correlations.pdf', height = 10, width = 10)
corrplot(habit_cors, method = 'color')
dev.off()
```

```{r}
orig_subs = read.csv('../4_roi_analysis/guessDG89.csv', stringsAsFactors = FALSE) %>%
  mutate(., prev_studied = 1)
```

# Put habit together with demographics, write to csv
```{r}
# SLOPES
habit_slopes_master = left_join(demog, habit_slopes, by = 'name') %>%
  left_join(., orig_subs, by = 'name') %>%
  mutate(scanner = ifelse(wave == 3, '2', '1'),
         blockBin = ifelse(Block == 1, 'first', 'notFirst')) 

habit_slopes_master_comps = dplyr::filter(habit_slopes_master, group != 'PI', group != 'Foster')

# HALVES
habit_halves_master = left_join(demog, habit_halves, by = 'name') %>%
  left_join(., orig_subs, by = 'name') %>%
  mutate(scanner = ifelse(wave == 3, '2', '1'),
         blockBin = ifelse(Block == 1, 'first', 'notFirst')) %>%
  dplyr::select(., everything(), reactivity = value)

habit_halves_master_comps = dplyr::filter(habit_halves_master, group != 'PI', group != 'Foster')

# SINGLE TRIALS

all_habit_trials_master = left_join(demog, all_habit_trials, by = 'name') %>%
  left_join(., orig_subs, by = 'name') %>%
  mutate(scanner = ifelse(wave == 3, '2', '1'),
         blockBin = ifelse(Block == 1, 'first', 'notFirst')) 


all_habit_trials_master_comps = dplyr::filter(all_habit_trials_master, group != 'PI', group != 'Foster')
```

# Save out spreadsheets
```{r}
# slopes
write.csv(habit_slopes_master_comps, 'compiled_data/habit_slopes_master_comps.csv', row.names = FALSE)
write.csv(habit_slopes_master, 'compiled_data/habit_slopes_master_everyone.csv', row.names = FALSE)

# halves
write.csv(habit_halves_master_comps, 'compiled_data/habit_halves_master_comps.csv', row.names = FALSE)
write.csv(habit_halves_master, 'compiled_data/habit_halves_master_everyone.csv', row.names = FALSE)

# single trials
write.csv(all_habit_trials_master_comps, 'compiled_data/habit_trials_master_comps.csv', row.names = FALSE)
write.csv(all_habit_trials_master, 'compiled_data/habit_trials_master_everyone.csv', row.names = FALSE)
```

# Quick Habit Block Model
```{r}
dplyr::filter(habit_halves_master_comps, set == 'bilateral_no_gsr_fear') %>%
  ggplot(data = ., aes(x = Age, y = reactivity, color = half)) +
  geom_point() +
  geom_line(aes(group = interaction(Subject, half)), alpha = .5) +
  facet_wrap('blockBin') +
  stat_smooth(method = 'lm') +
  theme_bw()


samp = dplyr::filter(habit_halves_master_comps, set == 'bilateral_no_gsr_fear')
mod_block = brms::brm(data = samp, reactivity ~ half*blockBin*ageCenter + motion + (half|ageCenter), chains = 1)
summary(mod_block)

brms::conditional_effects(mod_block)


pred_frame = expand.grid(ageCenter = -7:10, blockBin = c('first', 'notFirst'), half = c('half1', 'half2'), motion = 0)

preds = fitted(mod_block, newdata = pred_frame, re_formula = NA) %>%
  cbind(pred_frame, .)  %>%
  dplyr::mutate(half = ifelse(half == 'half1', 'Trials 1-12', 'Trials 13-24'),
                blockBin = ifelse(blockBin == 'first', 'Block 1', 'Block 2 or 3'),
                Age = ageCenter + habit_halves_master_comps$meanAge[1]) %>%
  dplyr::select(Trials = half, everything())

ggplot(preds, aes(x= Age, y = Estimate, color = Trials, fill = Trials)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_ribbon(aes(ymin = Q2.5, ymax = Q97.5), color = NA, alpha =.5) +
  geom_line() +
  facet_grid(~blockBin) +
  theme_bw() +
  labs(y = 'Estimated Amygdala Reactivity')
```

```{r}
dplyr::filter(habit_halves_master_comps, set == 'bilateral_no_gsr_neut') %>%
  ggplot(data = ., aes(x = Age, y = reactivity, color = half)) +
  geom_point() +
  geom_line(aes(group = interaction(Subject, half)), alpha = .5) +
  facet_wrap('blockBin') +
  stat_smooth(method = 'lm') +
  theme_bw()


samp_neut = dplyr::filter(habit_halves_master_comps, set == 'bilateral_no_gsr_fear')
mod_block_neut = brms::brm(data = samp_neut, reactivity ~ half*blockBin*ageCenter + motion + (half|ageCenter), chains = 1)

brms::conditional_effects(mod_block_neut)


pred_frame = expand.grid(ageCenter = -7:10, blockBin = c('first', 'notFirst'), half = c('half1', 'half2'), motion = 0)

preds_neut = fitted(mod_block_neut, newdata = pred_frame, re_formula = NA) %>%
  cbind(pred_frame, .)  %>%
  dplyr::mutate(half = ifelse(half == 'half1', 'Trials 1-12', 'Trials 13-24'),
                blockBin = ifelse(blockBin == 'first', 'Block 1', 'Block 2 or 3'),
                Age = ageCenter + habit_halves_master_comps$meanAge[1]) %>%
  dplyr::select(Trials = half, everything())

ggplot(preds_neut, aes(x= Age, y = Estimate, color = Trials, fill = Trials)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_ribbon(aes(ymin = Q2.5, ymax = Q97.5), color = NA, alpha =.5) +
  geom_line() +
  facet_grid(~blockBin) +
  theme_bw() +
  labs(y = 'Estimated Amygdala Reactivity')
```
